### 2013-07-06 paper.tex
Added discussion section with error tolerance subsection

>>>>

\section{Discussion}
\subsection{Error tolerance}
As seen in table \ref{heights} either when the vertical tilt angle is very wide, 
standing close to the tree, or very narrow, standing far away, leads to error. I
t's not clear what is causing this but there a two possibl reasons. The first one is
that because of the short focal length of the camera and overall poor quality when 
compared to a real camera, causes various forms of distrotion, especially around the 
edges of the image. When the person is standing close to the tree so the vertical tilt 
angle is over 45\degree, the points tend to lie exactly there, around the edges of 
the image. The distortion then affects these points causing the pixel measurements 
to be incorrect. The other problem occurs in the direct opposite situation, when 
the person is standing far away and the angle is very narrow. Naturally what happens 
is that the resolution of the camera just isn't high enough and the pixel measurements 
just aren't accurate anymore. However most of this distortion seems to only affect the 
vertical measurements because when looking at table \ref{widths} it is clearly seen that 
the readings do not stray much at all from their actual values. Despite this the deviation 
in the height readings still alters the volume calculations.
\subsection{Limitations}
\subsection{Future development}
\subsection{Future development}
